Indexed Containers

### 2011-05-10 journal/paper.tex
Various changes

We'll also require a notion of propositional equality, in Agda this is defined via a data-type:

@@

>>>>

We'll also require a notion of propositional equality. To simplyfy the presentation of some definitions later on, we will employ a heterogeneous equality.
This can be defined in Agda via a data-type:

@@

Most of the time our equalities will be homogeneous, however, so we introduce a short hand for this:

\begin{hscode}\SaveRestoreHook
\column{B}{@{}>{\hspre}l<{\hspost}@{}}%
\column{E}{@{}>{\hspre}l<{\hspost}@{}}%
\>[B]{}\Varid{\char95 ≡\char95 }\;\in\;\{\mskip1.5mu \Conid{A}\;\in\;\Conid{Set}\mskip1.5mu\}\;\rightarrow\;\Conid{A}\;\rightarrow\;\Conid{A}\;\rightarrow\;\Conid{Set}{}\<[E]%
\\
\>[B]{}\Varid{a}\;\equiv\;\Varid{b}\;\mathrel{=}\;\Varid{a}\;\cong\;\Varid{b}{}\<[E]%
\ColumnHook
\end{hscode}\resethooks

It is also known that homogeneous and heterogeneous equality have the same 
strength, so all the definitions employing our equality could also be encoded in
a theory with only homogeneous equality.
